Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-26 ms.rmd
Completed first paragraph

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (Figure \@ref(fig:fig1)B) amounting to a `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) reduction in freshwater and a `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) reduction in marine environments. Considering acute responses of animals acclimated to high temperatures is generally slightly elevated compared to cold acclimated animals ($\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change, on average.

>>>>

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (Figure \@ref(fig:fig1)B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, Figure  \@ref(fig:fig1)B). Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change.
